\cvsection{Projects}
\begin{cventries}
  \cventry
    {Topics in Deep Learning with Prof. Schuurmans}
    {Hierarchical BiGAN using Wasserstein Distance and
the Concrete Distribution}
    {1/2017 -- 4/2017}
    {
      \begin{cvitems}
        \item[>>] Derived a Wasserstein formulation of bidirectional GANs and investigated hierarchical and discrete extensions.
      \end{cvitems}
    }
  \cventry
    {Probabilistic Graphical Models with Prof. Greiner}
    {Structured Adversarial Inference and Learning}
    {1/2017 -- 4/2017}
    {
      \begin{cvitems}
        \item[>>] Proposed and implemented a method of inference in graphical models using adversarial networks.
      \end{cvitems}
    }
  \cventry
    {Introduction to Machine Learning with Prof. Greiner}
    {Completing Tensors with Indian Buffet Processes}
    {9/2016 -- 12/2016}
    {
      \begin{cvitems}
		\item[>>] Extended an MCMC algorithm to estimate missing values in tensors using an Indian Buffet Process prior.
      \end{cvitems}
    }
  \cventry
    {Honours Essay Supervised by Prof. Xu}
    {Exchange Rate Duration Under a Markov-Switching Multifractal: A GMM Approach}
    {1/2016 -- 4/2016}
    {
      \begin{cvitems}
      	\item[>>] Derived a Generalized Method of Moments for the Markov-Switching Multifractal duration model.
      \end{cvitems}
    }
    \cventry
    {Topics in Econometrics with Prof. Tao Chen}
    {Dealing with Zeros in Duration Data: A Nonparametric Approach}
    {1/2016 -- 4/2016}
    {
      \begin{cvitems}
        \item[>>] Developed a nonparametric imputation method for duration data that leverages inherent long range dependencies.
      \end{cvitems}
    }
    % \cventry
    % {Topics in Financial Econometrics with Prof. Dinghai Xu}
    % {Forecasting Exchange Rates Using AT-GARCH and Oil Prices}
    % {9/2015 -- 12/2015}
    % {
    %   \begin{cvitems}
    %     \item[>>] Implemented an asymmetric threshold GARCH volatility model to predict CAD/USD exchange rate using oil prices.
    %   \end{cvitems}
    % }
\end{cventries}

