\cvsection{Work Experience}
\begin{cventries}
  \cventry
    {Huawei Technologies Co., Ltd.}
    {Research Associate, Noah's Ark Lab}
    {01/2021 -- 12/2021}
    {
      \begin{cvitems}
        \item[>>] Supervisor: Jun Luo
        \item[>>] Researching auto-curriculum and generalization in
        reinforcement learning, with applications to autonomous vehicles.
      \end{cvitems}
    }

  \cventry
    {University of Alberta}
    {Teaching Assistant, Department of Computer Science}
    {01/2019 -- Present}
    {
      \begin{cvitems}
        \item[>>] Organized discussion groups and worksheets for new introductory reinforcement learning course.
        \item[>>] Guided students through projects and group assignments for foundations in information retrieval.
      \end{cvitems}
    }

  \cventry
    {University of Alberta}
    {Research Assistant, Department of Computer Science}
    {08/2018 -- Present}
    {
      \begin{cvitems}
      \item[>>] Supervisor: Dale Schuurmans 
      \item[>>] Researching methods that bridge the gap between online and batch
      reinforcement learning
      \end{cvitems}
    }

  \cventry
    {University of Alberta}
    {Teaching Assistant, Department of Mathematical and Statistical Sciences} {09/2016 -- 04/2018}
    {
      \begin{cvitems}
        \item[>>] Led help sessions in Introduction to Applied Statistics, Statistics I/II, Applied Regression Analysis and Time Series Analysis.
        \item[>>] Provided one on one assistance with assignments for first and second year classes at the Decima Robinson Support Centre.
      \end{cvitems}
    }

  \cventry
    {University of Alberta}
    {Research Assistant, Department of Mathematical and Statistical Sciences}    {05/2017 -- 07/2018}
    {
      \begin{cvitems}
        \item[>>] Supervisor: Ivor Cribben
        \item[>>] Implemented Gaussian process and deep learning methods to classify patients based on fMRI data using TensorFlow.
        \item[>>] Developed stochastic variational methods for recurrent neural network parameterized kernels in Gaussian process classification.
      \end{cvitems}
    }

\end{cventries}
